Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-04-10 paper/ms.tex
added new text

\begin{abstract}
We use simulations and recent observations to find the characteristic
mass of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies
at a redshift of $z=3.1$. The method is based on matching the
statistics for the number density cosmic variance between different
observed and mock fields. We build a model for LAEs on top of a large N-body
cosmological simulation (Bolshoi) where the basic principle is that a dark
matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
mass is found withing a certain range mass range delimited by two
threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
hundreds of mock catalogs in a thourough exploration of the parameter
space of this model. These catalogs are constructed in such a way as
to reproduce the spatial correlation between the different observed
fields. We find that the models that best match the observed cosmic
variance statistics are those with halo masses in the range $M_{\rm
  min}=$ and $M_{\rm max}=$ with and occupation fraction that scales
as $f_{\rm occ}=$ with the minimum mass. We find that the angular
correlation function is in agreement with the observational
constraints mostly due to the cosmic variance in the small angular
fields where this statistics has been computed so far. We also present
predictions for future measurements of the correlation function on
larger continous fields. We make available the mock data for the best
models in a public repository.  
\end{abstract}

@@

@@

As a prediction,

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
\end{center} f
\caption{ mean ACFs   and their correponding standard deviation (error bars)  of some selected models in different mass ranges
over the 7 subfields of the SSA22 field (left) and the entire 12 field sample (rigth) using the
match configuration. \label{figure:correlation_match} }

@@

\section{Conclusions}
In this \documentname we have constrained the preferred mass for dark matter
halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
method that matches the cosmic variance in the surface
density number of LAEs from differente observed fields. From this we
are able to constrain the mass range of dark matter halos hosting LAEs
to be in the range $<M_{\rm h}<$ and a corresponding occupation fraction
that escales as $f_{\rm occ} = M_{\rm min}$ with the minium halo mass
defining the halo mass range.

In this letter, this estimate is based on a large Nbody simulation
where we select a range a fraction of halos in a given mass range to
host LAEs. We explicitly construct mock observations to derive
statistics that can be compared against observations.

 The method is based on making an estimate of the cosmic
variance from different observed fields. Based on a Nbody simulation,
we select the range of halo masses, $M_{\rm min}<M_{\rm h}<M_{\rm
  max}$, and the fraction of these halos, $f_{\rm occ}$, that could
host LAEs being compatible witht the cosmic variance constraints.

We have used a large volume cosmological N-body simulation that allows
us to extract $210$ sub-boxes each of which has a comparable
volume to the field of view observed by Yamada et al. 2012. The
comparison of the observed number density distribution against the
results from our model is based on three different ways of
constructing mock surveys. The first reproduces the spatial
correlation between the $12$ observational fields, the second breaks
this spatial correlation while keeping the number of fields and the
third one simply includes all the $210$ sub-boxes.

>>>>

\begin{abstract}
We use simulations and recent observations to find the characteristic
mass of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies
at a redshift of $z=3.1$. The method is based on matching the
statistics for the number density cosmic variance between observed and
mock fields. We build a model for LAEs on top of a large N-body
cosmological simulation (Bolshoi) where the basic principle is that a
dark matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
mass is found withing a certain range mass range delimited by two
threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
hundreds of mock catalogs in a thourough exploration of the parameter
space of this model. These catalogs are constructed in such a way as
to reproduce the spatial correlation between the different observed
fields. We find that the models that best match the observed cosmic
variance statistics are those with halo masses in the range $M_{\rm
  min}=$ and $M_{\rm max}=$ with and occupation fraction that scales
as $f_{\rm occ}=$ with the minimum mass. We find that the angular
correlation function is in agreement with the observational
constraints mostly due to the cosmic variance in the small angular
fields where this statistics has been computed so far. We also present
predictions for future measurements of the correlation function on
larger continous fields. We make available the mock data for the best
models in a public repository.  
\end{abstract}

@@

From these tests we conclude that the ACF on small fields does not
provide additional constraints to further select models for halos
hosting LAEs. The reason is that cosmic variance is large and the
statistical uncertainties on the ACF render almost any model
compatible with the observational constraints.

@@

We also present the ACF in the case of the full SSA22
region which has been homogeneously observed by \citep{Yamada2012}. To
this date the observational ACF has not been reported in the
litereature, therefore our calculations can be considered as
predictions.

In Figure X we present the results for the models. The full list of
these correlation functions can be found in the the data repository
for this paper in \verb"github".

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
\end{center} f
\caption{ mean ACFs   and their correponding standard deviation (error
  bars)  of some selected models in different mass ranges over the 7
  subfields  f the SSA22 field (left) and the entire 12 field sample
  (rigth) using thematch
  configuration. \label{figure:correlation_match} }

@@

\section{Conclusions}
In this \documentname we constrain the preferred mass for dark matter
halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
method that matches the cosmic variance in the surface
density number of LAEs from differente observed fields to mock fields
based on a simplified model with three basic parameters. The halo
masses that define the halos where LAEs can be found, $M_{\rm
  min}<M_{\rm h}<M_{\rm max}$, and the fraction of the halos in this
range that are actully occupied, $f_{\rm occ}$. After a thorugh
exploration of the paremeter space we are able to constrain the mass
range of dark matter halos hosting LAEs to be in the range $<M_{\rm
  h}<$ and a corresponding occupation fraction that escales as $f_{\rm
  occ} = M_{\rm min}$.

In this letter, our estimates are based on a large volume, high
resolution, dark matter only Nbody simulation. From the halo catalogs
in the simulation a fraction of halos in a given mass range to
host LAEs. We use this information to construct mock observations to
derive the statistics that can be compared against observations. The
spatial information in this catalogs is also kept, which allows us to
compute angular correlation functions and include these results in our
analysis.

We simulation allows us to extract $210$ sub-boxes each of which has a
comparable volume to the individual fields of view observed by
\cite{Yamada2012}. The comparison of the observed number density
distribution against the results from our model is based on three
different ways of constructing mock surveys. The first reproduces the
spatial correlation between the $12$ observational fields ({\texttt
  match}), the second breaks this spatial correlation while keeping
the number of fields ({\texttt random}) and the third one simply
includes all the $210$ sub-boxes ({\texttt full}). We find that the
methods {\texttt match} and {\texttt random} allow a larger set of
models than the {{\texttt random}} method. We do not find a
significant difference between the two first methods.

Including additional observational constraints on the occupation
fraction allows us to reduce the range of allowed halo masses to be in
a narrower range of $<M_{\rm h}<$. Including the information from the
angular correlation function (ACF) does not allows us to impose
further constraints. This is due to the scatter in the ACF due to the
cosmic variance on the field observed by XXX
